---
params:
   kind: 0
   prm: NULL
pagetitle: Accenter -- documentation
title: "\0"
author: Nikita Platonov
link-citations: true
bibliography: platt.bib
LLLbibliography: C:/platt/article/platt.bib
csl: https://nplatonov.github.io/platt3.csl
date: "`r paste(format(file.mtime('question.Rmd'),'Updated: %Y-%m-%d %H:%M.'))`"
output:
   bookdown::html_document2:
      mathjax: NULL
      base_format: rmarkdown::html_vignette
      css: https://nplatonov.github.io/html_vignette.css
      self_contained: false
      number_sections: no
---

<style>
   body {
      margin: 1em auto;
      max-width: 790px;
   }
   .references {
      margin-top: 3em;
   }
   table td, table th {
      padding-left: 4px;
      padding-right: 4px;
   }
</style>

```{r init, include=FALSE}
knitr::opts_chunk$set(fig.align="center",echo=FALSE,message=FALSE,cache=TRUE
                     ,root.dir="C:/tmp")
require(shiny)
if (!("shiny" %in% loadedNamespaces()))
   'icon' <- function(name) paste("<",name,">")
res <- params$prm
kind <- params$kind
```

"Accenter" is Shiny application to analyse results of [Marxan](http://marxan.net/)) [@marxan.net; @Marxan2009]. This is improvement instrument of GIS identification tools.

Licence: MIT.

Based on subset of PAMPAN project. All data used here are prepared by Nikita Platonov. Data, which were prepared for PAMPAN, have no restiction for use out of PAMPAN project.

Structure is by vertical menu bar^[Not available for small screen size, e\.g\. mobile devices].

+ `r icon("bars")` Main

   Main workspace. Available for any screens. Seratated by horizontal menu (*tabs*):
   
   + `r icon("globe")` Map
   
      Available parameters using select list with choosing a single item.
      
      + Select region

         + Manual selection (digitizing polygons, lines and points for cells choice)

         + Predefined selection (choose one from list)
      
      + Select scenario
      
      + Select projection
      
         Projections are limited by EPSG codes [@proj4]: 3571, 3572, 3573, 3574, 3575, 3576.

   
   + `r icon("dashboard")` Review
      
      + Verbal statistics about selected cells and reached targets.
      
      + Visual statistics.
      
      + Map of cells, which are selected using region coverage.
   
   + `r icon("th-list")` Details
      
      Table with columns:

      + CF code
      
      + CF name

      + ...
     
      ```{r}
      ret <- NULL
      if (kind!=0) {
         da <- res
         ret <- knitr::kable(head(da)
                            ,caption="Example of table head rows (not formatted)")
      }
      ret
      ```


+ `r icon("question")`
   
   This documentation.

+ `r icon("info")`
   
   Brief description and information about author(s).

+ `r icon("user")`
   
   Link to author(s)

+ `r icon("github")`
   
   Link to Github repository.
