---
params:
   kind: 0
   prm: NULL
   bib: C:/platt/article/platt.bib
pagetitle: Accenter -- documentation
title: "[]{style=\"display: none;\"}"
author: "Nikita Platonov"
link-citations: true
bibliography: "`r params$bib`"
csl: https://nplatonov.github.io/platt3.csl
date: "`r paste(format(file.mtime('question.Rmd'),'Updated: %Y-%m-%d %H:%M.'))`"
output:
   bookdown::html_document2:
      mathjax: NULL
      base_format: rmarkdown::html_vignette
      css: https://nplatonov.github.io/html_vignette.css
      self_contained: false
      number_sections: no
---

<style>
   body {
      margin: 1em auto;
      max-width: 790px;
   }
   .references {
      margin-top: 3em;
   }
   table td, table th {
      padding: 3px 12px;
   }
   .tab, .menu {
      padding: 2px 10px;
      border: 1px solid #9ae;
      border-radius: 3px;
   }
   .tab {
      border-bottom-style: none;
   }
   .menu {
      border-right-style: none;
   }
   td .menu, td .tab {
      line-height: 1.8;
   }
   .example {
      color: orange;
      display: `r ifelse(params$kind==0,"none","inline")`
   }
</style>

```{r init, include=FALSE}
knitr::opts_chunk$set(fig.align="center",echo=FALSE,message=FALSE,cache=TRUE
                     ,root.dir="C:/tmp")
require(shiny)
if (!("shiny" %in% loadedNamespaces()))
   'icon' <- function(name) paste("<",name,">")
res <- params$prm
kind <- params$kind
tabMap <- paste0("[",as.character(icon('globe'))," Map]{.tab}")
tabReview <- paste0("[",as.character(icon('dashboard'))," Review]{.tab}")
tabTable <- paste0("[",as.character(icon('th-list'))," Details]{.tab}")
tabProp <- paste0("[",as.character(icon('map'))," Prop]{.tab}")
menuQuestion <- paste0("[",as.character(icon('question')),"]{.menu}")
menuMain <- paste0("[",as.character(icon('bars')),"]{.menu}")
```

## Accenter


"Accenter" is Shiny application to analyse results of [Marxan](http://marxan.net/) [@marxan.net; @Marxan2009]. This instrument expands deskop GIS identification tools^[e. g. QGIS [@QGIS]] and ***accent***uates on analysis of Marxan data strata based on spatial predefined and interactive requests. Named with ***er***-suffix as a reference to *instrument* and contradiction to accentor: *analyst/end-user*.

Licence: MIT.

### Glossary

```{r}
da <- data.frame()
da <- rbind(da,data.frame(name="Marxan",desc="An instrument fo spatial planning"))
da <- rbind(da,data.frame(name="Scenario",desc="Configuration, which is used to run Marxan"))
da <- rbind(da,data.frame(name="Selection",desc="Area of interest for spatial analysis"))
da <- rbind(da,data.frame(name="Region",desc="Study area"))
da <- rbind(da,data.frame(name=paste0("[",as.character(icon("paw"))," Menu item]{.menu}"),desc="Sidebar menu"))
da <- rbind(da,data.frame(name=paste0("[",as.character(icon("cannabis"))," Tab item]{.tab}"),desc="Top-side tabs"))
colnames(da) <- c("Term","Definition/description")
knitr::kable(da,format="html",escape=FALSE,format.args="line-height: 2.5;")
```

### Installation and usage

Shiny application with shiny-dashboard GUI:

+ [shinyapps.io](#) application. See also [PAMPAN application](https://wwfrussia.shinyapps.io/platini) without restrictions on under WWF Russia account

+ Run application on your local computer.

### Get started

Scenario, selection and projection are selected randomly^[If selection is manually, digitizing is requered at first].

Tab `r tabMap` is active, any of `r tabReview``r tabTable` can be selected.

Clicking of `r menuQuestion` shows this manual.

### User interface

Structure is by vertical menu bar^[Not available for small screen size, e\.g\. mobile devices].

+ `r menuMain` Main workspace. Available for any screens. Seratated by horizontal menu (*tabs*):
   
   + `r tabMap`
   
      Available parameters using select list with choosing a single item.
      
      + Select region

         + Manual selection (digitizing polygons, lines and points for cells choice)

         + Predefined selection (choose one from list).
      
         [Predefined or manual selection `r if (exists("input")) dQuote(input$rpath)` is detected in your configuraion.]{.example}
      + Select scenario.
        
        [Scenario `r if (exists("input")) dQuote(input$spath)` is selected in your configuration.]{.example}
      
      + Select projection.
      
        Projections are limited by EPSG codes [@proj4]: 3571, 3572, 3573, 3574, 3575, 3576. This is the same projection class with varios longitude of origin.
        
        [`r if (exists("input")) dQuote(input$epsg)` is selected in your configuration.]{.example}

   
   + `r tabReview`
      
      + Verbal statistics about selected cells and reached targets.
      
      + Visual statistics.
      
      + Map of cells, which are selected using region coverage.
   
   + `r tabTable`
      
      Table with columns:

      + CF code
      
      + CF name

      + ...

   + `r tabProp`
      
      Map of selected characteristics or property of input data.
      
      ```{r}
      ret <- character()
      if (params$kind>0) {
         da <- res
         ret <- knitr::kable(head(da)#,format.args="class='example'"
                            ,caption="Example of table head rows (not formatted)")
      }
      ret
      ```


+ `r menuQuestion`: Application manual.

+ [`r icon("info")`]{.menu}: Brief description and information about author(s).

+ [`r icon("user")`]{.menu}: Link to author(s)

+ [`r icon("github")`]{.menu}: Link to Github repository.

### Known problems

+ `r tabMap`: Duration of map rendering depends on number of Marxan planning units (POLYGONS geometry)

+ `r tabMap`: Perhaps, map rendering can be optimized due to reducing of re-rendering

+ `r tabTable`: Sometimes values are not rounded

+ `r tabProp`: Slow rendering due to no data aggregation

### What's new

+ `r Sys.Date()`

  *ongoing...*

+ 2019-09-15

  Branching supports one-level recursion in format \<project\>/\<version\>, with optional \<version\> and separated by "/" symbol.


+ 2019-08-30

  Added `r tabProp` tab.

+ 2019-08-28

  Added abbreviated "Representative/Distinctive" column into `r tabTable` table.

  `r tabMap`: Added input for selection Marxan output between **frequency** among set of runs and **best run**.

+ 2019-08-23

  Plotly boxes and bars for comparison between all region and selected area(s).

+ 2019-06-26

  Supporting branches via /?branch=%s request in URL

+ 2019-06-25

  Documentation is created and associated with `r menuQuestion` menu
